Information in sounds and letters in English, French and German speech

### 2019-08-30 surprisal/Phonemes/Phones.Rmd
reverse and shuffled prov surprisals

---
title: "Information in sounds and letters in English, French and German speech"
author: Josef Klafka and Dan Yurovsky 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: false
    number_sections: true
    theme: lumen
    toc_float: false
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

@@

```{r read-data}
all_data <- read_feather(here("Data/all_data.feather"))
adult_phonemes <- read_feather(here("Data/adult_phonemes.feather"))
```

@@

```{r plot-hist-helper}
plot_hists <- function(select_language = "English", select_rep = "letter") {

@@

```{r plot-curve-helper}
plot_curves <- function(select_language = "English", select_rep = "letter", 
                        select_gram = "Unigram") {
  all_data %>%
    filter(language == select_language, rep == select_rep,
           gram == select_gram) %>%
    filter(word_length %in% 2:6) %>%
    ggplot(aes(x = order, y = mean_s)) +
    facet_grid(. ~ word_length, 
               labeller = as_labeller(function(x) paste0("Length ", x))) +
    geom_point() +
    geom_line() +
    xlab(paste0(str_to_sentence(select_rep), " Position")) +
    ylab("Average information") + 
    ggtitle(paste0("Information in ", select_language, " ", 
                   select_rep, "s by ",select_rep, " position - ", select_gram))
}
```

>>>>

---
title: "Information in sounds and letters in English, French and German speech"
author: Josef Klafka and Dan Yurovsky 
date: "`r Sys.Date()`"
output: pdf_document

editor_options: 
  chunk_output_type: console
---

@@

```{r read-data, include=F}
all_data <- read_feather(here("Data/all_data.feather"))
adult_phonemes <- read_feather(here("Data/adult_phonemes.feather"))
```

@@

```{r plot-hist-helper, include=F}
plot_hists <- function(select_language = "English", select_rep = "letter") {

@@

```{r plot-curve-helper, include=F}
plot_curves <- function(select_language = "English", select_rep = "letter", 
                        select_gram = "Unigram") {
  all_data %>%
    filter(language == select_language, rep == select_rep,
           gram == select_gram) %>%
    filter(word_length %in% 2:6) %>%
    ggplot(aes(x = order, y = mean_s)) +
    facet_grid(. ~ word_length, 
               labeller = as_labeller(function(x) paste0("Length ", x))) +
    geom_point() +
    geom_line() +
    xlab(paste0(str_to_sentence(select_rep), " Position")) +
    ylab("Average information") + 
    ggtitle(paste0("Information in ", select_language, " ", 
                   select_rep, "s by ",select_rep, " position - ", select_gram))
}
```
